ECCCos from the Black Box:\\ Faithful Explanations through\\ Energy-Constrained Conformal Counterfactuals

### 2023-12-11 paper/tables.Rmd
more updating

```{r}
# Aggregate by run:
tab <- dt[
    generator %in% generators,
    .(
      val_group = mean(value),
      std_group = sd(value)
    ),
    .(dataname, generator, model, variable, run, source)
]

# Aggregate accross runs:
tab <- tab[
    generator %in% generators,
    .(
      value =  sprintf("%1.2f ± %1.2f", mean(val_group), sd(val_group)),
      val = mean(val_group),
      std = sd(val_group)
    ),
    .(dataname, generator, model, variable, source)
]

@@

```{r}
# Aggregate by run:
tab_valid <- dt_valid[
    generator %in% generators,
    .(
      val_group = mean(value),
      std_group = sd(value)
    ),
    .(dataname, generator, model, variable, run, source)
]

# Aggregate accross runs:
tab_valid <- tab_valid[
    generator %in% generators,
    .(
      value = sprintf("%1.2f ± %1.2f", mean(val_group), sd(val_group)),
      val = mean(val_group),
      std = sd(val_group)
    ),
    .(dataname, generator, model, variable, source)
]

>>>>

```{r}
# Aggregate by run:
tab <- dt[,
    .(
      val_group = mean(value),
      std_group = sd(value)
    ),
    .(dataname, generator, model, variable, run, source)
]

# Aggregate accross runs:
tab <- tab[,
    .(
      value =  sprintf("%1.2f ± %1.2f", mean(val_group), sd(val_group)),
      val = mean(val_group),
      std = sd(val_group)
    ),
    .(dataname, generator, model, variable, source)
]

@@

```{r}
# Aggregate by run:
tab_valid <- dt_valid[,
    .(
      val_group = mean(value),
      std_group = sd(value)
    ),
    .(dataname, generator, model, variable, run, source)
]

# Aggregate accross runs:
tab_valid <- tab_valid[,
    .(
      value = sprintf("%1.2f ± %1.2f", mean(val_group), sd(val_group)),
      val = mean(val_group),
      std = sd(val_group)
    ),
    .(dataname, generator, model, variable, source)
]
